### 2020-01-30 README.Rmd
Added sf pkg to README
Added initial attempt at define_buffer()

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 16/2,
  fig.height = 9/2,
  message = FALSE,
  warning = FALSE
)
```

@@

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
```

@@

```{r, cache=TRUE}
# Read in Big Woods census data from 2008 & 2014
bw_2008 <- 
  "https://deepblue.lib.umich.edu/data/downloads/z603qx485" %>% 
  read_delim(delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )
bw_2014 <- 
  "https://deepblue.lib.umich.edu/data/downloads/1831ck00f" %>% 
  read_delim(delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )

@@

```{r, cache=TRUE}
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  )

@@

```{r, cache=TRUE}
census_df1 <- bw_2008
census_df2 <- bw_2014
id <- "treeID"

@@

```{r, cache=TRUE}
census_df1 <- scbi_2013
census_df2 <- scbi_2018
id <- "stemID"

@@

If the above doesn't work, the go back to what we used for PLOS paper.

@@

```{r, cache = TRUE}

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 16/2,
  fig.height = 9/2,
  message = FALSE,
  warning = FALSE,
  cache = TRUE
)
```

@@

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
# library(blockCV)
```

@@

```{r}
# Read in Big Woods census data from 2008 & 2014
bw_2008 <- 
  "https://deepblue.lib.umich.edu/data/downloads/z603qx485" %>% 
  read_delim(delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )
bw_2014 <- 
  "https://deepblue.lib.umich.edu/data/downloads/1831ck00f" %>% 
  read_delim(delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )

@@

```{r}
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  )

@@

```{r}
census_df1 <- bw_2008
census_df2 <- bw_2014
id <- "treeID"

@@

```{r}
census_df1 <- scbi_2013
census_df2 <- scbi_2018
id <- "stemID"

@@

* If the above doesn't work, the go back to what we used for PLOS paper.
* Consider making `growth_df` an `sf` object

@@

```{r, cache = TRUE}
square <- tibble(
  x = c(0,0,1,1),
  y = c(0,1,1,0)
) %>% 
  sf_polygon()
buffer <- square %>% 
  st_buffer(dist = -0.1)
ggplot() +
  geom_sf(data = square) +
  geom_sf(data = buffer, col="red")

# Bigwoods study region boundary polygon
bw_boundary <- bigwoods_study_region %>% 
  sf_polygon()

# Buffer polygon
bw_buffer <- bw_boundary %>%
  st_buffer(dist = -25)

# Sample of 5000 trees
set.seed(76)
bw_trees_sample <- bw_growth_df %>% 
  sample_n(5000) %>% 
  select(x = gx, y = gy) %>% 
  st_as_sf(coords = c("x", "y"))

index <- st_intersects(bw_trees_sample, bw_buffer, sparse = FALSE)
bw_trees_sample <- bw_trees_sample %>% 
  mutate(buffer = index)

# Plot
ggplot() +
  geom_sf(data = bw_boundary) +
  geom_sf(data = bw_buffer, col="red") +
  geom_sf(data = bw_trees_sample, aes(col=buffer), size = 0.5)
```
